Full-day, in home validation of infant body position measurements from inertial sensors

### 2023-02-17 manuscript.Rmd
organize code chunks

## Goal 2: Assess classification accuracy over long recordings
<!-- compiled_agreement, generated from analysis-part2 -->
```{r}
# Count up position totals and join into an agreement data frame
calculate_agreement <- function(ds) {
  model <- ds %>% count(file, pos) %>% 
    add_count(file, wt = n, name = "total") %>% 
    mutate(prop_model = n/total)
  human <- ds %>% count(file, code) %>% 
    add_count(file, wt = n, name = "total") %>% 
    mutate(prop_human = n/total)
  agree_group <- full_join(select(model, file, pos, prop_model), 
                     select(human, file, code, prop_human), 
                     by = c("file" = "file", "pos" = "code"))
  agree_group <- agree_group %>% mutate(prop_human = ifelse(is.na(prop_human), 0, prop_human),
                            prop_model = ifelse(is.na(prop_model), 0, prop_model))
  agree_group <- complete(agree_group, file, pos, fill = list(prop_human = 0, prop_model = 0))
}

@@

# difference_plot <- function(ds) {
#   ds %>% mutate(diff = prop_human - prop_model) %>% 
#   ggplot(aes(x = pos, y = diff, color = pos)) +
#   stat_summary() + 
#   scale_fill_manual(values = pal, guide = "none") + 
#   ylab("Prediction Difference (%)") + ylim(-.5, .5) + xlab("")
# }
```

```{r part2overall, warning=FALSE, fig.cap="Overall agreement between human-coded body position and model-predicted body position in the long-delay period. Agreement for group models is shown in (A) and agreement for individual models is shown in (B). Plots are shown separately for each body position with a reference line that indicates perfect agreement; each point in a plot represent data for a single participant.", fig.align="center", fig.width=7, fig.height=6.5}
# GROUP MODEL PART 2 AGREEMENT
pt2_group <- read_csv("data/compiled_agreement_position.csv") %>% 
  filter(nap_period == 0 & exclude_period == 0 & !is.na(code) & !is.na(pos)) %>% 
         mutate(pos = factor(pos, levels = pos_levels))
pt2_split <- read_csv("data/compiled_agreement_split.csv") %>% 
  filter(nap_period == 0 & exclude_period == 0 & !is.na(code) & !is.na(pos)) %>% 
         mutate(pos = factor(pos, levels = pos_levels))

@@

```{r, pt2overalltable}
pt2corr_with_outliers <- map_dfc(agree, ~ .x %>% group_by(pos) %>% cor_test(vars = c("prop_model", "prop_human")) %>% select(pos, cor)) %>% select(-`pos...3`)
pt2corr_without_outliers <- map_dfc(agree, ~ .x %>% filter(file != "107/3", file != "104/1") %>% group_by(pos) %>% cor_test(vars = c("prop_model", "prop_human")) %>% select(pos, cor)) %>% select(-`pos...1`,-`pos...3`)
pt2corr <- bind_cols(pt2corr_with_outliers, pt2corr_without_outliers)
rm(pt2corr_with_outliers)
rm(pt2corr_without_outliers)

#Overall
group_agree_cor <- cor_test(agree$group, vars = c("prop_model", "prop_human")) %>% pull(cor)
split_agree_cor <- cor_test(agree$split, vars = c("prop_model", "prop_human")) %>% pull(cor)
group_agree_cor_noout <- agree$group %>% filter(file != "107/3", file != "104/1") %>% 
  cor_test(vars = c("prop_model", "prop_human")) %>% pull(cor)
split_agree_cor_noout <- agree$split %>% filter(file != "107/3", file != "104/1") %>%
  cor_test(vars = c("prop_model", "prop_human")) %>% pull(cor)
overall_row <- tibble("Overall", group_agree_cor, split_agree_cor, group_agree_cor_noout, split_agree_cor_noout)
colnames(overall_row) <- colnames(pt2corr)
pt2corr <- bind_rows(pt2corr, overall_row)
apa_table(pt2corr, col.names = c("Position", "Group", "Individual", "Group", "Individual"), col_spanners = list(`With Outliers` = c(2, 3), `Without Outliers` = c(4, 5)),
          midrules = 5)

# difference_plots <- map(agree, difference_plot)
# difference_plots <- map2(difference_plots, c("A. Group Models", "B. Individual Models"), ~ .x + ggtitle(.y))
# difference_plots[[1]] + difference_plots[[2]]

@@

>>>>

## Goal 2: Assess classification accuracy over long recordings
<!-- compiled_agreement, generated from analysis-part2 -->

```{r part2overall, warning=FALSE, fig.cap="Overall agreement between human-coded body position and model-predicted body position in the long-delay period. Agreement for group models is shown in (A) and agreement for individual models is shown in (B). Plots are shown separately for each body position with a reference line that indicates perfect agreement; each point in a plot represent data for a single participant.", fig.align="center", fig.width=7, fig.height=6.5}

# PART 2 AGREEMENT
pt2_group <- read_csv("data/compiled_agreement_position.csv") %>% 
  filter(nap_period == 0 & exclude_period == 0 & !is.na(code) & !is.na(pos)) %>% 
         mutate(pos = factor(pos, levels = pos_levels))
pt2_split <- read_csv("data/compiled_agreement_split.csv") %>% 
  filter(nap_period == 0 & exclude_period == 0 & !is.na(code) & !is.na(pos)) %>% 
         mutate(pos = factor(pos, levels = pos_levels))

outlier_files <- c("107/3", "104/1", "106/1")
filter_outliers <- . %>% filter(!(file %in% outlier_files))

# Count up position totals and join into an agreement data frame
calculate_agreement <- function(ds) {
  model <- ds %>% count(file, pos) %>% 
    add_count(file, wt = n, name = "total") %>% 
    mutate(prop_model = n/total)
  human <- ds %>% count(file, code) %>% 
    add_count(file, wt = n, name = "total") %>% 
    mutate(prop_human = n/total)
  agree_group <- full_join(select(model, file, pos, prop_model), 
                     select(human, file, code, prop_human), 
                     by = c("file" = "file", "pos" = "code"))
  agree_group <- agree_group %>% mutate(prop_human = ifelse(is.na(prop_human), 0, prop_human),
                            prop_model = ifelse(is.na(prop_model), 0, prop_model))
  agree_group <- complete(agree_group, file, pos, fill = list(prop_human = 0, prop_model = 0))
}

@@

@@

```{r, pt2overalltable}
pt2corr_with_outliers <- map_dfc(agree, ~ .x %>% group_by(pos) %>% cor_test(vars = c("prop_model", "prop_human")) %>% select(pos, cor)) %>% select(-`pos...3`)
pt2corr_without_outliers <- map_dfc(agree, ~ .x %>% filter_outliers %>% group_by(pos) %>% cor_test(vars = c("prop_model", "prop_human")) %>% select(pos, cor)) %>% select(-`pos...1`,-`pos...3`)
pt2corr <- bind_cols(pt2corr_with_outliers, pt2corr_without_outliers)
rm(pt2corr_with_outliers)
rm(pt2corr_without_outliers)

#Overall
group_agree_cor <- cor_test(agree$group, vars = c("prop_model", "prop_human")) %>% pull(cor)
split_agree_cor <- cor_test(agree$split, vars = c("prop_model", "prop_human")) %>% pull(cor)
group_agree_cor_noout <- agree$group %>% filter_outliers %>% 
  cor_test(vars = c("prop_model", "prop_human")) %>% pull(cor)
split_agree_cor_noout <- agree$split %>% filter_outliers %>%
  cor_test(vars = c("prop_model", "prop_human")) %>% pull(cor)
overall_row <- tibble("Overall", group_agree_cor, split_agree_cor, group_agree_cor_noout, split_agree_cor_noout)
colnames(overall_row) <- colnames(pt2corr)
pt2corr <- bind_rows(pt2corr, overall_row)
apa_table(pt2corr, col.names = c("Position", "Group", "Individual", "Group", "Individual"), col_spanners = list(`With Outliers` = c(2, 3), `Without Outliers` = c(4, 5)),
          midrules = 5)

@@

#Bins
pt2corr_with_outliers <- map_dfc(agree_bins, ~ .x %>% group_by(pos) %>% cor_test(vars = c("prop_model", "prop_human")) %>% select(pos, cor)) %>% select(-`pos...3`)
pt2corr_without_outliers <- map_dfc(agree_bins, ~ .x %>% filter_outliers %>% group_by(pos) %>% cor_test(vars = c("prop_model", "prop_human")) %>% select(pos, cor)) %>% select(-`pos...1`,-`pos...3`)
pt2corr <- bind_cols(pt2corr_with_outliers, pt2corr_without_outliers)
rm(pt2corr_with_outliers)
rm(pt2corr_without_outliers)

group_agree_cor <- cor_test(agree_bins$group, vars = c("prop_model", "prop_human")) %>% pull(cor)
split_agree_cor <- cor_test(agree_bins$split, vars = c("prop_model", "prop_human")) %>% pull(cor)
group_agree_cor_noout <- agree_bins$group %>% filter_outliers %>% 
  cor_test(vars = c("prop_model", "prop_human")) %>% pull(cor)
split_agree_cor_noout <- agree_bins$split %>% filter_outliers %>%
  cor_test(vars = c("prop_model", "prop_human")) %>% pull(cor)
overall_row <- tibble("Overall", group_agree_cor, split_agree_cor, group_agree_cor_noout, split_agree_cor_noout)
colnames(overall_row) <- colnames(pt2corr)
pt2corr <- bind_rows(pt2corr, overall_row)
apa_table(pt2corr, col.names = c("Position", "Group", "Individual", "Group", "Individual"), col_spanners = list(`With Outliers` = c(2, 3), `Without Outliers` = c(4, 5)),
          midrules = 5)

difference_plot <- function(ds) {
  ds <- mutate(ds, diff = prop_human - prop_model)
  ggplot(filter_outliers(ds), aes(x = pos, y = diff, color = pos, group = file)) +
  stat_summary(position = position_dodge(.4), alpha = .7) +
  stat_summary(data = filter(ds, file %in% c("107/3", "104/1", "106/1")), position = position_dodge(.4), alpha = .7, color = "darkgray") +
  scale_color_manual(values = pal, guide = "none") +
  coord_cartesian(ylim = c(-1, 1)) + xlab("") + 
  scale_y_continuous(name = "Prediction Difference (min)", breaks = seq(-1, 1, .2), labels = seq(-10, 10, 2), minor_breaks = waiver())
}
difference_plots <- map(agree_bins, ~ difference_plot(.x))
difference_plots <- map2(difference_plots, c("A. Group Models", "B. Individual Models"), ~ .x + ggtitle(.y))
difference_plots[[1]] + difference_plots[[2]]

### 2023-02-17 manuscript.tex
organize code chunks

>>>>

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:pt2overalltable}}

\begin{tabular}{lllll}
\toprule
 & \multicolumn{2}{c}{With Outliers} & \multicolumn{2}{c}{Without Outliers} \\
\cmidrule(r){2-3} \cmidrule(r){4-5}
Position & Group & Individual & Group & Individual\\
\midrule
Held & -0.02 & 0.16 & 0.55 & 0.63\\
Prone & 0.97 & 0.83 & 0.97 & 0.84\\
Sitting & 0.72 & 0.93 & 0.91 & 0.97\\
Supine & 0.84 & 0.93 & 0.94 & 0.97\\
Upright & 0.84 & 0.93 & 0.99 & 0.94\\ \midrule
Overall & 0.79 & 0.90 & 0.95 & 0.96\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table}

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-2}}

\begin{tabular}{lllll}
\toprule
 & \multicolumn{2}{c}{With Outliers} & \multicolumn{2}{c}{Without Outliers} \\
\cmidrule(r){2-3} \cmidrule(r){4-5}
Position & Group & Individual & Group & Individual\\
\midrule
Held & 0.45 & 0.44 & 0.57 & 0.56\\
Prone & 0.96 & 0.81 & 0.96 & 0.88\\
Sitting & 0.72 & 0.93 & 0.91 & 0.93\\
Supine & 0.75 & 0.93 & 0.90 & 0.94\\
Upright & 0.93 & 0.95 & 0.97 & 0.95\\ \midrule
Overall & 0.80 & 0.92 & 0.92 & 0.94\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table}

\begin{verbatim}
## Warning: Removed 10 rows containing missing values (`geom_segment()`).
\end{verbatim}

\begin{verbatim}
## Warning: Removed 5 rows containing missing values (`geom_segment()`).
\end{verbatim}

\begin{verbatim}
## Warning: Removed 10 rows containing missing values (`geom_segment()`).
\end{verbatim}

\begin{verbatim}
## Warning: Removed 5 rows containing missing values (`geom_segment()`).
\end{verbatim}

\includegraphics{manuscript_files/figure-latex/unnamed-chunk-2-1.pdf}
